A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-05 manuscript.Rmd
move introduction of hypothetical research question

We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).
To guide the reader through all steps of a research project, we will use an exemplary research question:

@@

At the heart of a PAC lies the planned analysis.
We suggest writing a function that captures the full process of testing a research question beginning from the dataset.
This is a simple example:

@@

We decided to draw non-normal data to test how well our procedure performed under non-optimal situations.
Specifically, we draw from a $\Chi^2$-distribution, where in one group we add difference that conforms to a standardized effect size.
This simulated dataset fits perfectly into our planned analysis:

>>>>

We have structured the tutorial with a _learning by doing_ approach in mind, such that readers can follow along at their own computers.
We explicitly encourage readers to try out all R commands for themselves.
Unless stated otherwise, all code blocks are meant to be run in the statistical programming language R (tested with version `r with(R.version, paste0(major, ".", minor))`).

@@

To guide the reader through all steps of a research project, we will use an exemplary research question:

At the heart of a PAC lies the planned analysis.
We suggest writing a function that captures the full process of testing a research question that receives a dataset as input.
For the hypothetical research question, we could for example plan to conduct a simple Student's t-test with Welch's correction an the average of machiavillism items between the gender groups.
As an example of data dependend decisions we included a rank transformation if the skewness greater than 1, converting the t-test to a supposedly more robust Mann–Whitney–Wilcoxon test.[^caution-mww]
This example is suboptimal with regard to several criteria (untested assumption of measurement invariance, underestimation of effectsize in presence of measurement error, overestimation of effectsize for highly skewed distributions), we merely choose it for didactic purposes because similar procedures a widely used (@horton reports that 26% of all studies employ a t-test and 27% employ a rank based alternative in the New England Journal of Medicine in 2005).

[^caution-mww]: The Mann–Whitney–Wilcoxon is **not** more robust than the Welch corrected t-test for reasonably large sample sizes. The interested reader can use the provided code for the simulation to verify that the t.test provides unbiased effect sizes but the Mann–Whitney–Wilcoxon overestimates effect size with increasing sample size and skewness.

@@

We decided to draw non-normal data to test how well our procedure performed under non-optimal situations.
Specifically, we draw from a $\chi^2$-distribution, where in one group we add difference that conforms to a standardized effect size.
This simulated dataset fits perfectly into our planned analysis:
